Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-02-15 ms.tex
more work on the intro

Ground-based gravitational-wave interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe.  The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India.  Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!).  In addition to the ....(do we want to review emission mechanisms?)

In this paper we present a method of rapid sky localization that makes use of Bayesian methods.  It differs from

>>>>

Ground-based gravitational-wave interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe.  The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India.  Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!).  In addition to being an efficient source of gravitational waves, the neutron star may be tidally shredded before merging, providing fuel for an electromagnetic counterpart.  The short-lived accretion flow may power a collimated relativistic jet, resulting in a short gamma-ray burst and an X-ray afterglow if it is aligned with the line of sight. An optical afterglow may follow minutes to hours later as the jet plows into the interstellar medium. As surrounding neutron-rich ejecta decay radioactively, an optical 'kilonova' may be visible after ~1 day. Finally, as the ejecta plow into the interstellar medium, a faint radio afterglow will occur on a timescale of years.

There is therefore a strong case for performing electromagnetic followups of these sources of gravitational waves.  Indeed, the final science run of the intitial LIGO and Virgo instruments saw the first joint search for gravitational waves from compact binaries and their electromagnetic counterparts....

In this paper we present a method of rapid sky localization that makes use of Bayesian methods.  It differs from...
